---
title: "NYC Airbnb"
author: "Jeff Goldsmith"
date: "10/9/2017"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
```

## Data import

I'll load the tidyverse and the dataset. I'm also doing a bit of editing and renaming to make my life easier. 

```{r}
library(tidyverse)

airbnb_data = read_csv("./data/nyc_airbnb.zip") %>%
  mutate(rating = review_scores_location / 2) %>%
  rename(boro = neighbourhood_group)
```

## Understanding variables

Next I'll do a bit of inspection to make sure I understand the data structure.

```{r}
# View(airbnb_data)
str(airbnb_data)

airbnb_data %>%
  count(boro)

airbnb_data %>%
  count(room_type)
```

## Brainstorming questions

### Does rating vary by neighborhood, room type, or both?

First I'll create a table to look at rating by boro.

```{r}
airbnb_data %>%
  group_by(boro) %>% 
  filter(!is.na(rating)) %>%
  summarize(median_rating = median(rating),
            mean_rating = mean(rating),
            sd_rating = sd(rating))
```

Next I'll try some visual displays.

```{r}
airbnb_data %>%
  ggplot(aes(x = boro, y = rating)) + 
  geom_violin(bw = .1)

airbnb_data %>%
  ggplot(aes(x = room_type, y = rating)) + 
  geom_violin(bw = .1)
```

Finally, I'm interested in the `room_type` variable. Rating didn't seem to vary much across this variable, but I'd still like to examine this and boro at the same time. 

The chunk below creates a table, and then uses `knitr::kable()` to format the output.

```{r}
airbnb_data %>%
  group_by(boro, room_type) %>% 
  filter(!is.na(rating)) %>%
  summarize(mean_rating = mean(rating)) %>%
  spread(key = boro, value = mean_rating) %>%
  knitr::kable()
```

### Do hosts with more listings have higher or lower ratings?


### Where are rentals located?

I'm going to use [latitude](https://en.wikipedia.org/wiki/Latitude) and [longitude](https://en.wikipedia.org/wiki/Longitude) to plot the location of rentals. I always get lat and mixed up, and it seems like the person who put these data together did as well ...

```{r}
airbnb_data %>%
  ggplot(aes(x = longitude, y = latitude)) +
  geom_point()
```

Next I'll try to clean this up a bit and use other aesthetic mappings. For simplicity, I'll also focus on Manhattan.

```{r, fig.asp = 1}
airbnb_data %>%
  filter(boro == "Manhattan") %>% 
  ggplot(aes(x = longitude, y = latitude, color = rating)) +
  geom_point(alpha = .1) + 
  scale_colour_gradient(low = "red", high = "green",
  space = "Lab", na.value = "grey50", guide = "colourbar") +
  coord_cartesian() + 
  theme_classic()
```

We can learn quite a bit from this -- there are fewer rentals in some neighborhoods of Manhattan than others, and there seems to be a slight decrease in rating for rentals farther north than downtown. 

### Other questions

There are several questions we didn't get to:

* How is price related to other variables?
* How are descriptions related to number of reviews?
* Which rentals make the most money?
* What's different about low-availability rooms?

Of these, the question dealing with descriptions is one we're not in a position to handle yet -- that involves parsing character strings, which we'll get to shortly. The others we could at least explore using the tools we have at our disposal now.


## Discussion

Need a discussion.